Symbolic music generation using Mamba architecture

### 2024-06-14 docs/paper/paper.tex
add synth data to paper

\begin{table}[t] \centering
    % Podpis tabeli umieszczamy od góry
    \caption{Model comparison \cite{mamba}}
    \label{tab:comparison}

    % Tabela z trzema kolumnami:
    % dwie wyrównanie do środka [c], a ostatnia do prawej [r]
    % szerokość kolumn automatyczna (równa szerokości tekstu)
    \resizebox{\linewidth}{!}{\begin{tabular}{| c | c | c | c |} \hline
        Architecture       		& Complexity    			& Memory   		& Performance \\ \hline\hline
        Transformer      			&    	 $ O(N^2)$ 		& $O(N^2)$     		& great    \\ \hline
        RNN     				&    	$O(N)$		 	& $O(N)$    		& poor     \\ \hline
        SSM      				&  	$O(N)$ 			& $O(N)$     		& poor     \\ \hline
       Selective SSM (Mamba)     &    	 $O(N)$ 			& $O(N)$    		& great.  \\ \hline
        % Komórka o szerokości dwóch kolumn, wyrównana do prawej
        % Przypisy dolne w tabelach wstawiamy przez \tablefootnote
        % \multicolumn{2}{|r|}{Suma\tablefootnote{Table footnote.}} & 123,45 \\ \hline
    \end{tabular}}
\end{table}

@@

\section{Training Setup}
TODO
\section{Experiments}
TODO
\section{Conclusions}
TODO
% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

>>>>

@@

\section{Training Setup}
TODO
\section{Experiments}
\subsection{Synthetic Data}
To first check that our training setup is correct we decided to overfit the model to synthetic data. For this purpose we generated sequence $0, 1, ..., 1999$ and trained the tried to make model generate it after receiving 0 token as imput. During the training loss  quickly approached zero. When testing the model it managed to generate the entire sequence correctly, abeit it requred tunung the generation function's parameters.

 \begin{figure}[!htbp]
    \centering \includegraphics[width=\linewidth]{../assets/synth_data_train.png}
    \caption{ Loss during training on synthetic data}
    \label{fig:synth}
\end{figure}

\section{Conclusions}
TODO
% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}
